---
title: "Publications"
format: html
execute:
  echo: false         # hide the R code in the rendered page
---

<!-- visible explanatory text -->
<blockquote style="color:#444444;">
  <strong>About this list</strong><br>
   Citation counts are pulled from <strong>Google Scholar</strong>.<br>
   Bibliographic metadata (title, year, journal, type) comes from <strong>ORCID</strong> (<em>ORCID iD 0000‑0002‑7972‑7928</em>).<br>
   <em>Data last refreshed:</em> <strong>`r format(file.info("publications.csv")$mtime, "%d %B %Y")`</strong>
</blockquote>

```{r}
```{r}
library(readr)
library(DT)
library(stringr)

# Read the saved CSV
pubs <- read_csv("publications.csv", show_col_types = FALSE)

# Keep & rename desired columns
pubs_display <- pubs[, c("Year", "Author", "Title", "Journal", "Citations")]
colnames(pubs_display) <- c("Year", "Authors", "Title", "Journal", "Citations")

# Bold 'S Canavan' in Authors
pubs_display$Authors <- str_replace_all(
  pubs_display$Authors,
  fixed("S Canavan"),
  "<strong>S Canavan</strong>"
)

# Interactive table (turn off HTML escaping so bold shows)
datatable(
  pubs_display,
  escape = FALSE,          # allow HTML tags in table cells
  options = list(
    pageLength = 15,
    autoWidth  = TRUE,
    order      = list(list(0, "desc"))   # sort by Year (newest first)
  ),
  rownames = FALSE
)
```