---
title: "Tools"
format:
  html:
    page-layout: full
    toc: true
    toc-depth: 2
    toc-location: left
    code-tools: true
execute:
  echo: true
  warning: false
  message: false
---

```{r setup, include=FALSE}
library(suezalla)
library(ggplot2)
library(showtext)
library(sysfonts)
suezalla_fonts()
```

## suezalla: a custom ggplot2 theme and colour palette

`suezalla` is a lightweight R package that provides:

- Custom `ggplot2` themes: `theme_magazine()`, `theme_latex()`, `theme_zombie()`, `theme_academic1940()`, and `theme_academic1940_pattern()`
- Several curated colour palettes inspired by polaroids, jam jars, retro aesthetics, zombies, and classic scientific graphics
- Pattern fill utilities for `ggpattern`, including `suezalla_academic_style()`
- Custom scale functions: `scale_colour_suezalla()` and `scale_fill_suezalla()`

These tools help you create clean, consistent, or stylistically bold visualizations with minimal effort.

## Installation

```{r}
# If not already installed
# install.packages("devtools")

# Install suezalla
# devtools::install_github("sucanavan/suezalla")
```

## Available palettes

```{r palette-preview, results='asis', echo=FALSE}
palettes <- list(
  polaroid  = c("#45AAB4", "#038DB2", "#206491", "#F9637C", "#FE7A66", "#FBB45C"),
  vibrant   = c("#FFC567", "#FD5A46", "#00995E", "#FB7DA8", "#552CB7", "#058CD7"),
  jam       = c("#FBC9BE", "#DB7B65", "#ECB865", "#695356", "#255F63"),
  corporate = c("#23C2A2", "#EC3431", "#FBDE21", "#138ABD", "#9BBAFA"),
  lively1   = c("#ED5565", "#FFCE54", "#48CFAD", "#5D9CEC", "#FC6E51", "#A0D468", "#4FC1E9", "#AC92EC"),
  lively2   = c("#DA4453", "#F6BB42", "#37BC98", "#4A89DC", "#E9573F", "#8CC152", "#3BAFDA", "#967ADC"),
  retro     = c("#E7363C", "#F56438", "#FCAB20", "#59AC99", "#3E446E"),
  autumn    = c("#388388", "#4ABFBD", "#8AB17D", "#E9C46A", "#F4A261", "#E76F51"),
  zombie    = c("#B3B3B3", "#F56438", "#59AC99"),
  academic  = c("#000000", "#1A1A1A", "#666666", "#B3B3B3", "#FFFFFF"),
  npg       = c("#E64B35", "#4DBBD5", "#00A087", "#3C5488", "#F39B7F",
                "#8491B4", "#91D1C2", "#DC0000", "#7E6148", "#B09C85")
)

cat("<table><thead><tr><th>Palette</th><th>Colours</th></tr></thead><tbody>")
for (name in names(palettes)) {
  colors <- palettes[[name]]
  color_boxes <- paste0(
    "<span style='display:inline-block;width:20px;height:20px;background-color:", colors,
    ";margin-right:3px;border:1px solid #ccc' title='", colors, "'></span>"
  )
  cat(sprintf("<tr><td><code>%s</code></td><td>%s</td></tr>", name, paste(color_boxes, collapse = "")))
}
cat("</tbody></table>")
```

## Using palettes in code

```{r}
# Return 4 discrete colours from the 'jam' palette
suezalla_palette("jam", n = 4)

# Return 10 interpolated colours from the 'autumn' palette as a gradient
suezalla_palette("autumn", n = 10, type = "continuous")
```

## Fonts

The `suezalla` package auto-loads:

- **Roboto** from Google Fonts for `theme_suezalla()`
- **XKCD** (if available locally) for `theme_zombie()`
- **Abhaya Libre**, **Latin Modern Roman**, and **CMU Serif** for academic themes

These are handled automatically via `sysfonts` and `showtext` when the package is attached.

## Quick examples

### LaTeX academic plot

```{r}
ggplot(mtcars, aes(x = mpg, y = wt, shape = factor(carb))) +
  geom_point(size = 2, stroke = 0.4) +
  theme_latex() +
  labs(
    title = "Car efficiency by weight",
    x = "Miles per Gallon",
    y = "Weight",
    shape = "Carburetors"
  )
```

### Academic 1940

```{r}
ggplot(mtcars, aes(x = mpg, y = wt, shape = factor(carb))) +
  geom_point(size = 2, stroke = 0.4, color = "black", fill = "white") +
  scale_shape_manual(values = c(0, 1, 2, 3, 4, 5)) +
  theme_academic1940() +
  labs(
    title = "Car efficiency by weight",
    x = "Miles per Gallon",
    y = "Weight (1000 lbs)",
    shape = "Carburetors"
  )
```

### Academic pattern style

```{r}
df <- aggregate(wt ~ cyl, data = mtcars, FUN = mean)
df$cyl <- factor(df$cyl)

ggplot(df, aes(x = cyl, y = wt, fill = cyl, pattern = cyl)) +
  theme_academic1940_pattern(n = 3)
```

### Magazine theme

```{r}
ggplot(mtcars, aes(x = wt, y = mpg, colour = factor(cyl))) +
  geom_point(size = 3) +
  scale_colour_suezalla(palette_name = "corporate") +
  theme_magazine() +
  theme(
    axis.ticks = element_line(size = 0.3),
    axis.ticks.length = unit(3, "pt")
  ) +
  labs(
    title = "Car efficiency by weight",
    x = "Weight",
    y = "Miles per Gallon",
    colour = "Cylinders"
  )
```

### Zombie theme

```{r}
ggplot(mtcars, aes(y = wt, x = mpg)) + 
  geom_point(aes(fill = factor(cyl), size = cyl), shape = 21, alpha = 0.8) + 
  scale_fill_suezalla(palette_name = "zombie") + 
  theme_zombie() +
  labs(
    title = "Car efficiency by weight",
    x = "Weight",
    y = "Miles per Gallon",
    colour = "Cylinders"
  )
```